Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Intro to LB

The adversary constructs components of nodes, and $\OPT$ never splits them.
The adversary observes the actions of an online algorithm, and if it splits the components at any moment, the adversary issues

>>>>

In this section, we provide a lower bound $\Omega(k\cdot \ell)$ for the competitive ratio of any deterministic algorithm.
The minimum cluster capacity for the construction to remain correct is $3$.

The adversary constructs components of nodes, and issues only requests among nodes in the same component.
If an online algorithm splits the components at any moment, the adversary issues requests to split pairs of nodes.
We utilize the fact that the online algorithm does not know the components of the adversary, and it may split some components while evicting nodes.
On the other hand, $\OPT$ never splits the components.
